---
title: "SP500"
output: html_document
---

## Introduction

For MSDS 6306 assignment 11 goal is to to modify SP500.R file so that we are able to download, analyse and plot data, followed by generating this markdown document and uploading work on github account. 

## Get Libraries

Get and load required libraries.

```{r lib, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
# these libraries are needed to run this analysis
#install.packages("tseries")
library(tseries)
```

## Setup Environment

Point to appropriate local directory for analysis.

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
# first set working directory
setwd("/home/kuroevan/Desktop/R-Projects/lab11/sp500")
getwd()
```

## Get Data

Get Data required for analysis.

```{r assingment, include=TRUE}
SNPdata <- get.hist.quote('^gspc',quote = "Close")
length(SNPdata)
```

## Analyze Data

Analyze Data by first doing a log trasformation and then calculating volatility. Use 3 different decay factors.

```{r analyze, include=TRUE}
SNPret <- log(lag(SNPdata)) - log(SNPdata)
length(SNPret)
SNPvol <- sd(SNPret) * sqrt(250) * 100
SNPvol
Vol <- function(d, logrets) {
  var = 0
  lam = 0
  varlist <- c()
  for (r in logrets) {
    lam = lam*(1-1/d) + 1
    var = (1-1/lam)*var + (1/lam)*r^2
    varlist <- c(varlist,var)
  }
  sqrt(varlist)
}
volest <- Vol(10,SNPret)
volest2 <- Vol(30,SNPret)
volest3 <- Vol(100,SNPret)
```

## Plot Data

Plot results overlaying volatility curves on data.

```{r plot, echo=TRUE}
plot(volest, type = "l")
lines(volest2,type = "l", col="red")
lines(volest3,type = "l", col="blue")
```

